---
title: "R Markdown Presentation & Plotly"
author: "Pedro Cortes dos Santos"
date: "23/02/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Summary

This project was created as part of the Developing Data Products course of the Coursera Data Science Specialization.

The goal of the project is to create  a web page presentation using R Markdown that features a plot created with Plotly. The webpage must contain the date that you created the document, and it must contain a plot created with Plotly.

## Heatmap - Daily Ozone Levels in New York

```{r, echo=TRUE}
library(datasets)
library(plotly)
library(reshape2)
data("airquality")  

airquality$Month = as.factor(airquality$Month)  
ozone_daily = airquality[, c(1, 5, 6)]  

ozone_daily = dcast(ozone_daily, Day ~ Month, value.var = "Ozone")
ozone_daily = as.matrix(ozone_daily[, -1])
colnames(ozone_daily) = c("May", "June", "July", "August", "September")

plot_ly(z = ozone_daily, colorscale = "Hot", x = colnames(ozone_daily), 
    type = "heatmap", colorbar = list(title = "Ozone Levels (parts per billion)")) %>% 
    layout(title = "Daily Ozone Levels in New York, May to September 1973", 
        xaxis = list(title = "Month"), yaxis = list(title = "Day"))
```

## Scatterplot - EuStockMarkets Daily Closing Price

```{r, echo=TRUE}
library(plotly)
data("EuStockMarkets")
df <- as.data.frame(EuStockMarkets)
df$time = 1:dim(df)[1]
xlab <- list(title = 'Time (Number of Days)')
ylab <- list(title = 'Closing Price')
plot_ly(data = df, x = ~time, y = ~DAX,
             type = 'scatter', mode = 'markers', name = 'DAX') %>%
    add_trace(y = ~SMI, type = 'scatter', mode = 'markers', name = 'SMI') %>%
    add_trace(y = ~CAC, type = 'scatter', mode = 'markers', name = 'CAC') %>%
    add_trace(y = ~FTSE, type = 'scatter', mode = 'markers', name = 'FTSE') %>%
    layout(xaxis = xlab, yaxis = ylab)
```